Towards Practical First-Order Model Counting

### 2025-02-06 doc/paper/paper.tex
Improve the introduction

\todo[inline,caption={}]{
  \begin{itemize}
    \item We would like to clarify that the main contribution of this work
          consists of everything needed to complement recursive function
          definitions with the necessary base cases. This process includes
          identifying the base cases and their corresponding sentences,
          transforming them (including applying a new smoothing procedure), and
          recursively reusing Crane. C++ code generation, although relatively
          straightforward, is crucial for the usability of the algorithm.
    \item Focus more on current work
  \end{itemize}
}

@@

In \cref{sec:preliminaries}, we cover some preliminaries, and in
\cref{sec:main}, we detail all our technical contributions. Finally, in
\cref{sec:experiments}, we present our experimental results, demonstrating
\Cranetwo{}'s performance compared to other FOMC algorithms, and, in
\cref{sec:conclusion}, we conclude the paper by discussing promising avenues for
future work.

>>>>

@@

The paper is structured as follows. \Cref{sec:preliminaries} covers the
necessary preliminaries including notation, terminology, and background
information about (W)FOMC and FOKC\@. \Cref{sec:main} describes all aspects of
\Cranetwo{}:
\begin{itemize}
  \item its overall structure and interactions with \textsc{Crane},
  \item how we identify a sufficient set of base cases for a recursive function,
  \item how we construct the sentence that `describes' each base case, and
  \item how function definitions are compiled into a C++ program with caching
        mechanisms that ensure efficiency.
\end{itemize}
Then, \cref{sec:experiments} presents our experimental results, demonstrating
\Cranetwo{}'s performance compared to other FOMC algorithms. Finally,
\cref{sec:conclusion} concludes the paper by discussing promising avenues for
future work.
